\chapter{Introduction}\label{C:intro}

\section{The Context}
Whiley is a programming language that mixes features from object orientated and functional languages. The aim of Whiley is to offer programmers language level code verification. Due to software failures being able to prove aspects of a program are important. This is no less true when developing for the web. With web based applications handling security and monetary transactions. Being able to prove that these types of program are working as intended is important. 
Web Assembly is a assembly language that has been created for running in the browser of all major browser developers. Its is being developed to be a compile target for languages that wish be run on the web. Its aim is to be fast and efficient. Currently Web Assembly is in the early stages of development, so feature such as garbage collection or debugging software have not been implemented. Web Assembly's main difference from other assembly languages is the tree structure use in the for its definition. 

\section{The Opportunity}
With the introduction of Web Assembly (wasm), Whiley now has a new compile target. Work has been done previously to compile Whiley to both JavaScript and ASM.js (a low level subset of JavaScript). While both languages work on the web, neither are assembly languages and as such are not made for being a compile target. With the development of Web Assembly whiley now has a appropriate compile target. This gives the opportunity to compare Web Assembly and JavaScript against each other, both being compiled from Whiley.

\section{Current Status}
The Whiley-to-WebAssembly translator is the step between Whiley's intermediary language (WyIL) and Web Assembly. Currently a WyIL file is passed to a Java implementation of a the translator which then parses it. The parsing creates an absract syntax tree of the file in wasm. That tree can then be written as a wasm file. With that Whiley applications can be run in browsers made by Google, Mozilla, and Microsoft \cite{8_wagner_2016}. To ensure that those files when created run correctly a test harness has been set up. There are 440 test (from the Whiley test suite) that are run, of which 241 pass. Of the test that have failed they have been codified and then divided up into sections of unimplemented, bugs and known features. Of these tests failed because of unimplemented functionality has the largest amount of tests. 

